---
output: 
  pdf_document:
    keep_tex: false
header-includes:
  - \usepackage{fullpage}
  - \usepackage{color}
  - \definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
  - \definecolor{lightblue}{rgb}{0.68, 0.85, 0.9}
  - \usepackage{booktabs}
  - \usepackage{sectsty} \allsectionsfont{\centering}
  - \usepackage{paralist} \let\itemize\compactitem
  - \usepackage[labelformat=empty]{caption}
params:
  region: "East Anglia"
  vers: vers
  price: price
  afford: afford
  plot_price: plot_price
  plot_afford: plot_afford
  bsadf_table_price: bsadf_table_price,
  bsadf_table_afford: bsadf_table_afford,
  autoplot_price: autoplot_price
  autoplot_afford: autoplot_afford
  crit: crit
title: "UKHO - `r params$region` - `r params$vers` Release"
fontsize: 12pt 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(exuber)
library(knitr)
options(knitr.table.format = "latex")
library(xtable)
library(patchwork)
```

This page provides figures for real house prices and house-price-to-disposable-income ratios (housing affordability) starting in 1975, exuberance statistics, as well as date-stamping of the specific periods of exuberance.

```{r plot, fig.align='center', fig.height=4, fig.width=7, message=FALSE}
p1 <- plot_price[[params$region]] +
  ggtitle("Real House Prices") +
  scale_custom(price, div = 4) +
  theme(plot.title = element_text())
p2 <- plot_afford[[params$region]] +
  ggtitle("Affordability Index") +
  scale_custom(afford, div = 4) +
  theme(plot.title = element_text())
p1 + p2
```

## Latest Statistics

```{r calc-statistics}
x1 <- calc_growth(price[[params$region]])
x2 <- calc_growth(afford[[params$region]])
```

```{r stat-html}
c(x1, x2) %>% 
  kable()
```

```{r stats-pdf, results='asis'}
cat(c("\\begin{table}[!htpb]
    \\begin{minipage}[t]{.5\\linewidth}
    \\centering
    \\begin{tabular}{c}
    Real House Price Change \\\\
    \\midrule",
    x1, "\\\\
    \\end{tabular}
    \\end{minipage}%
    \\begin{minipage}[t]{.5\\linewidth}
    \\centering
    \\begin{tabular}{c}
    Affordability Index Change \\\\
    \\midrule",
    x2, "\\\\
    \\end{tabular}
    \\end{minipage}
    \\end{table}"
))
```

\vfill

\center{\textit{ © 2020 Housing Observatory. All rights reserved}}

\newpage

# Financial Stability

```{r autoplot, fig.align='center', fig.height=4, fig.width=7, message=FALSE}
ap1 <- autoplot(price, select_series = params$region) +
  ggtitle("Real House Prices") +
  scale_custom(price, div = 4) +
  theme(plot.title = element_text())
ap2 <- autoplot(afford, select_series = params$region) +
  ggtitle("Affordability Index") +
  scale_custom(afford, div = 4) +
  theme(plot.title = element_text())
ap1 + ap2
```

## Latest Exuberance Indicators

```{r latest-exuberance-indicators, results='asis'}
ax1 <- round(tail(bsadf_table_price[[params$region]], 1),3)
ax2 <- round(tail(bsadf_table_afford[[params$region]], 1),3)
ax1_exuber <- if (ax1 > crit) "Exuberance" else "No Exuberance"
ax2_exuber <- if (ax2 > crit) "Exuberance" else "No Exuberance"
cat(c(
  "\\begin{table}[!htpb]
    \\begin{minipage}[t]{.5\\linewidth}
    \\centering 
    \\begin{tabular}{c}
    Real House Price (BSADF) \\\\
    \\midrule",
    ax1, "\\\\",
    "\\textbf{", ax1_exuber, "}\\\\",
    "\\end{tabular}
    \\end{minipage}%
    \\begin{minipage}[t]{.5\\linewidth}
    \\centering
    \\begin{tabular}{c}
    Affordability Index (BSADF) \\\\
    \\midrule",
    ax2, "\\\\",
    "\\textbf{",  ax2_exuber, "}\\\\",
    "\\end{tabular}
    \\end{minipage}
    \\end{table}"
))
```


## Date-Stamping Periods of Exuberance

```{r datestamp, results='asis'}

null_df <- data.frame("Start" = "","End" = "", "Duration" = "")

t1 <- kable(datestamp(radf_price, cv_price)[[params$region]] %||% 
           null_df,format = "latex", booktabs = TRUE)
          
t2 <- kable(datestamp(radf_afford, cv_afford)[[params$region]] %||% 
           null_df,format = "latex", booktabs = TRUE)

cat(c("\\begin{table}[!htpb]
    \\begin{minipage}[t]{.5\\linewidth}
      \\caption{Real House Prices}
      \\centering",
        t1,
    "\\end{minipage}%
    \\begin{minipage}[t]{.5\\linewidth}
      \\centering
        \\caption{Affordability Index}",
        t2,
    "\\end{minipage}
\\end{table}"
))

```






\vfill

\center{\textit{ © 2020 Housing Observatory. All rights reserved}}
