---
# title: "Latest Release: 2018 Q4"
geometry: "left=3cm,right=3cm,top=1.5cm,bottom=1cm"
runtime: shiny
output:
  pdf_document:
    pandoc_args: [
        "-V", "classoption=twocolumn"
    ]
  html_document: default
header-includes:
  - \usepackage{color}
  - \usepackage[dvipsnames]{xcolor}
---

\thispagestyle{empty}

<!-- ## Latest Release: 2018 Q4 -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r plots, include=FALSE}
autoplot_price <- readRDS("data/RDS/autoplot_price.rds")
plot_price <- readRDS("data/RDS/plot_price.rds")
```

###### Real House Price and Trend
```{r echo=FALSE}
library(ggplot2)
plot_price$UK
```

###### Some Graph

```{r echo=FALSE}
plot_price$UK 
```

###### Some Graph

```{r echo=FALSE}
autoplot_price$UK 
```

###### Some Graph

```{r echo = FALSE}
autoplot_price$UK
```

\newpage

### \textcolor{BrickRed}{Summary}

The growth rate of UK property  prices has been falling over 
the  last  two  quarters. The annual growth rate currently stands at 2.2%. This 
is the lowest growth rate of national housing prices since 2013 Q2. Furthermore, 
property prices in Greater London have fallen by nearly 2% over the last year. 
However, house prices have increased in all other regional markets. Overall, the 
regions that have experienced the highest property price inflation rates 
in the course of the last year are not in the South of the country: East 
Midlands(4.4%), West Midlands(4.2%),Wales(4%), and Scotland(3.1%).

### \textcolor{BrickRed}{Financial Stability}

The UK Housing Observatory has created this new series that will contribute to 
the analysis of the housing market and general economic conditions in the UK. 
HPU is an index of search results from five large newspapers in the UK. This 
index proxies for movements in house price uncertainty. We have now incorporated 
this seriesto the set of variables we employ in our forecast modelsbecause it 
helps improve their out-of-sample forecasting power."

\vspace{5mm}

### \textcolor{BrickRed}{Exuberance Indicators}

The Price-to-Income Ratio continues to be high for
historical standards, close to its all-time high in 2007. Despite the decrease 
in London house prices, the ratio has not declined substantially due to  the  
fall  in  real  income.  This  indicator  will  therefore  continue  to  be  a 
sourceof  concern  as pressure on indebted households does not show signs of
easing off.

\vspace{1cm}

### \textcolor{BrickRed}{Forecasting}

The prediction of the UK Housing Observatory is that the growth rate ofhouse prices 
in the national and the majority of regional markets will continue to dropin the 
course of 2018and the first half of 2019. We forecast a growth rate of about 1.7% 
inthe secondquarter of 2019. The forecasts  predict a similar pattern of house price 
behaviour in all regions  with a much stronger patter in Greater London. 
According to the forecasting results, the property prices in this region will 
experience negative growth, they will continue to decline during 2018 and the first 
quarter of 2019,  however  the  growth  in housing prices  is  predicted  to  build  
up  towards  the  end of  the following year. 
